% General notes:
% 1) All lines in a verse environment must end with \\, the last verse in a stanza
% must end in \\!

\documentclass[11pt, a4paper]{article} 

\usepackage{verse} 

\usepackage[T1]{fontenc} 
\usepackage{palatino}
%\usepackage{stix} % Alternative Stix fon

\setlength{\parindent}{0pt}

% Author styles
\newcommand{\poemauthorcenter}[1]{\nopagebreak{\centering\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem center aligned
\newcommand{\poemauthorright}[1]{\nopagebreak{\raggedleft\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem aligned right

\renewcommand{\poemtitlefont}{\normalfont\bfseries\large\centering} % Define the poem title style

\setlength{\stanzaskip}{0.75\baselineskip} % The distance between stanzas

\pagestyle{empty} % Stop page numbering through the document

\begin{document}

\poemtitle{Life Beginning}

\settowidth{\versewidth}{If you can} % Insert one of the average-sized verses, used for centering the poem

\begin{verse}[\versewidth]

%------------------------------------------------

Write \\
thoughts, \\
poetry, \\
a novel, \\
my theological beliefs. \\!

%------------------------------------------------

Read \\
classics, \\
modern literature, \\
essays, \\
study mathematics. \\!

%------------------------------------------------

Watch \\
foreign films, \\
my children,
movements in the woods \\
in the river. \\!

%------------------------------------------------

Find \\
my self, \\
my family, \\
my path, \\
life. \\!

%------------------------------------------------

How shall I use my time? Measure time? \\!

%------------------------------------------------

At one knot, life is mine to choose. \\ 
The ability to pursue passion. \\ 
Yet, unable to determine that passion. \\
Though capable of the discipline required to find, 
see that passion out. \\!

%------------------------------------------------

To observe \\
the night sky, \\
over a season, \\
from a single perception. \\

To observe \\
the individual, 
ours, \\
over a life, \\
yields no answers. \\

%------------------------------------------------

Over two years, \\
writing my life, \\
fictionalized, \\
a rambling disjointed memoir. \\
A recount of where life was, \\
is, \\
going. \\!

%------------------------------------------------

My reading will deepen. \\ 
Classics in literature, philosophy, history, theology, mathematics, science. \\
Training will change to run a 100 miler through the swamps, a 100 miler over the mountains. \\
Writing daily, drink whiskey nightly. \\!

%------------------------------------------------

Early morning fog are low clouds \\
Low clouds are fog in the late night \\
Fog envelopes the woods \\
Acting as the canopy \\
As the sky \\
The canopy \\
The sky \\
Shadows of trees in the fog \\
Fog \\
The moisture \\
A beard softens \\
Over a jog \\
In low clouds \\
Drops of water \\
In a beard \\
The fog \\
Droplets fall \\
Rain \\
Too heavy \\ 
For the edges \\!

%------------------------------------------------

Last weekend, I learned how to shot a rifle. \\
Prior it was the military. \\ 
Always rushed. \\
Enough time to see if you could load a round, fire a shot, hit a target. \\ 
At the range, in the rimfire corner, by myself for two hours. \\
Now I understand. \\
Load, unload, fix a jam, disassemble, clean, reassemble, fire. \\!

The next day I taught my daughter. 

A successful hunt, a lofty goal, a distant dream. To get a boat into the river, swamps, marsh, to fish, is the same. A distant dream.  

I want a farm, a flat boat for the rivers.

I want a cabin in Southeast Alaska. Live there three to five months out of the year. 

I'll write.

I'll find my voice.

%------------------------------------------------

Poetry
Will be an obscure fact
In a memoir
No one read
Published
Hundreds of years from now.

%------------------------------------------------

Until then, I will not cut my beard, until I have found the path, my direction. 
How many knots?

%------------------------------------------------

\end{verse}

%------------------------------------------------

\poemauthorright{J. Theriot} % Right-aligned author



\end{document}