\documentclass[11pt, sigconf, nonacm]{acmart}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2020}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{http://vldb.org/pvldb/format_vol14.html}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain} 

\begin{document}
\title{On \texit{Providence}}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Justin Theriot}

\maketitle

We define \textit{Providence} as the plan conceived in the mind of God, according to which He directs all creatures to their proper end. 
\ \\
\ \\
Before we discuss the significance of Providence we note that \textit{there is no moral obligation, so it is said, without a supreme law giver, and it is impossible to regard ourselves as a subject to a categorical more obligation unless this supreme lawgiver is first recognized.} Thus if we do not recognize God, as Lagrange stated, then the notion of Providence is irrelevant. The modern scientific argument on the basis of God as introduced by Stephen Hawking states that\textit{so long as the universe had a beginning, we could suppose it a had a creator. But if the universe is really completely self-contained, having no boundary or edge, it would have neither beginning nor end: it would simply be. What place, then, for a creator?} 
\ \\
\ \\
It matters little weather the Earth had a beginning in its revolution around the sun; what is necessary is for the sun to attract it now, and for the sun itself to be attracted by a more remote and actually existing center of attraction. There is a no succession either past or future but an everlasting present. The now that stands, not that flows away. Henceforth we are to discuss the matter of Providence based on the faith that God exists. 
\ \\
\ \\
With that being said, how are we to understand the plan of God as envisioned? Concisely, we are to lead simple lives, following God's commandments. A soul that \textit{is simple in its outlook, will be in all things enlightened, steadfast, loyal, sincere, and free from all duplicity.} The direction in which to lead our lives is straight forward yet it is we who create complexity as we have \textit{no thought for the future life; we believe that the just must be rewarded and the wicked punished even in this world.} An outlook that predates Job. We are motivated by immediate rewards where we are unable to envision a just future beyond our life on Earth, embodying an \textit{outlook of the fool who considers all things from their lowest standpoint reducing them} to the present life. We must remember, \textit{the end is first in the order of intention but last in order execution.} 
\ \\
\ \\
Bossuet reminds us, \textit{to the one tormented with all sorts of ideas about predestination that we must abandon ourselves to God, with the assurance that our salvation is infinitely more secure in God's hands than our own.} Even though we require clothes on our backs, food on our tables, and a roofs over our heads the work we conduct to provide for our needs should not be distorted by the individualistic or communist perspective. Balance between these conflicting viewpoints enable us to thrive. However, through our growth we must heed to \textit{possess the things of this world not as their servants but as their lords and not be enslaved by them as a miser by his wealth.} 
\ \\
\ \\
Furthermore, we cannot lead a life as God intended simply as an intellectual endeavour but through \textit{sanctifying grace, which is a participation in the Divine nature,} built not upon egoism, self-love, and divided interests as these often are \textit{no more than cloak to cover the deeper jealously and hatred within ourselves.} The disillusionment we are met with are permitted in order to direct our thoughts more and more to this supreme beauty and impel us to love it. Ergo our work must be founded on \textit{truly helping one another as thy journey on to eternal life.} \textit{The saints are seen by God and the angels, not by bodies or curious minds. God suffices them.} 
\ \\
\ \\
For this we must \textit{pray as the saints have prayed, cooperate in the saving not only of bodies but of souls...Rare indeed are the souls that attain to such perfection as this. And yet it is the goal at which we all must aim.} As \textit{the life of man upon Earth is warfare,} we must desire to \textit{contemplate in God the transcendent simplicity,} as pride will cripple him with reason driving him insane. 

\end{document}
\endinput
